MSDS Case Study 2 - Procrastination and HDI Data

### 2017-12-01 MSDS_CaseStudy2_Master.Rmd
Updated rmarkdown to fix some things as well as add the code necessary to have pretty tables

```{r custom packages}
if (!is.element("dplyr", installed.packages()[,1]))
  install.packages("dplyr",repos="http://cran.rstudio.com")
if (!is.element("ggplot2", installed.packages()[,1]))
  install.packages("ggplot2",repos="http://cran.rstudio.com")
if (!is.element("stringr", installed.packages()[,1]))
  install.packages("stringr",repos="http://cran.rstudio.com")
if (!is.element("rvest", installed.packages()[,1]))
  install.packages("rvest",repos="http://cran.rstudio.com")
if (!is.element("xml2", installed.packages()[,1]))
  install.packages("xml2",repos="http://cran.rstudio.com")
 if (!is.element("tidyr", installed.packages()[,1]))
  install.packages("tidyr",repos="http://cran.rstudio.com")
if (!is.element("curl", installed.packages()[,1]))
  install.packages("curl",repos="http://cran.rstudio.com")
if (!is.element("stargazer", installed.packages()[,1]))
  install.packages("stargazer",repos="http://cran.rstudio.com")
if (!is.element("stringi", installed.packages()[,1]))
  install.packages("stringi",repos="http://cran.rstudio.com")
```

@@

#Load libraries
library("dplyr")
library("rvest")
library("tidyr")
library("ggplot2")
library("stargazer")
library("ggpubr")
library("reshape2")
library("stringr")

@@

#Custom functions for Case Study 2
#Last modified 11/26/17

#Wrapper function for gsub that maintains object classes
gsubkeep = function(pattern='',replacement=NA,x, ignore.case=FALSE, perl=FALSE,
										fixed=FALSE, useBytes=FALSE) {
	if (is.null(dim(x)) && !is.null(class(x))) {
		colObj = x
		colClass = class(colObj)
		colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
									ignore.case=ignore.case,perl=perl,fixed=fixed,
									useBytes=useBytes)
		if (colClass == 'factor') {
			colObj = as.factor(colObj)
		} else { 
			colObj = as(colObj,colClass) 
		}
		x = colObj
	} else {
		for (i in 1:length(x)) {
			colObj = x[,i]
			colClass = class(colObj)
			colObj = gsub(pattern=pattern,replacement=replacement,x=colObj,
										ignore.case=ignore.case,perl=perl,fixed=fixed,
										useBytes=useBytes)
			if (colClass == 'factor') {
				colObj = as.factor(colObj)
			} else { 
				colObj = as(colObj,colClass) 
			}
			x[,i] = colObj
		}
	}
	return(x)
}

#Function that row-stacks the identified columns of a list of data frames
#Parameters: {x: list of data frames, elements: the particular data frames within x to stack, 
#             cols: the particular columns to stack, colname: names of the columns selected with cols parameter }
list_rowbind = function(x,elements=1:length(x),cols = columns(1:length(x[[1]])),
												colname = colnames(x[[1]])[cols]) {
	result = data.frame()
	for (i in elements) {
		append_df = x[[i]][,cols]
		colnames(append_df) = colname
		result = bind_rows(result,append_df)
	}
	return(result)
}

#Function that creates a list of indices and corresponding strings which match keywords
#Paratermers: {x: a vector (to be coerced to character) to search, findtext: a vector of keywords to look for}
match_list = function(x,findtext='') {
	findtext = as.character(findtext)
	x = tolower(as.character(x))
	result = list(length(findtext))
	for (i in 1:length(findtext)) {
		result[i] = list(cbind('Idx'=grep(findtext[i],x),'Match'=x[grep(findtext[i],x)]))
	}
	return(result)
}

@@

# 2A: Read in CSV
dataset_raw <- read.csv("C:\\SMU_INTRO_TO_DS\\CASESTUDY2\\Data\\Procrastination.csv")

@@

```{r Question4 Preliminary Analysis}

@@

# 4B:
#statistics table
stargazer(resp_full[,c('Age','Annual_Inc','HDI','DP_Avg','AIP_Avg','GP_Avg','SWLS_Avg')],type='text',
					summary.stat=c('n','min','p25','median','p75','max','mean','sd'))

@@

h1 = gghistogram(resp_full,x='Age',y='..count..',
								 bins=10,
								 fill='blue',
								 size=2,
								 title='Age',
								 color='white'
)

h1 + font('x.text',size=8)

h2 = gghistogram(resp_full,x='Annual_Inc',y='..count..',
								 bins=10,
								 fill='blueviolet',
								 size=2,
								 title='Ann Inc',
								 color='white'
)

h2 + font('x.text',size=10)

h3 = gghistogram(resp_full,x='HDI',y='..count..',
								 bins=5,
								 fill='cadetblue3',
								 size=2,
								 title='HDI',
								 color='white'
)

@@

h4 = ggboxplot(metrics,x='Variable',
							 y='Value',
							 color='Variable',
							 palette='jco',
							 size=1.5
)

h4 + font('x.text',size=10)

ggarrange(ggarrange(h1,h2,h3,ncol=3,labels=c('1','2','3')),
					h4,
					nrow=2,
					labels='4')

@@

# Frequencies per column 
# Unique distributions
# Gender
apply(resp_full["Gender"], 2, table)

# WorkStatus
apply(resp_full["Work_Status"], 2, table)

#Distributions across Gender and Work Status
with(resp_full, table(Gender, Work_Status))

top10Jobs

@@

countryCt <- count(resp_full, resp_full$Country_Res)
colnames(countryCt) <- c("Country", "Count")

sortedCC <- countryCt[order(countryCt$Count, decreasing = TRUE),]

print(sortedCC)

# 4E:

@@

viewMatch <- count(resp_full[which(resp_full$Self_Score == resp_full$Others_Score),])
print(viewMatch)

>>>>

```{r custom packages}
if (!is.element("dplyr", installed.packages()[,1]))
  install.packages("dplyr",repos="http://cran.rstudio.com")
if (!is.element("ggplot2", installed.packages()[,1]))
  install.packages("ggplot2",repos="http://cran.rstudio.com")
if (!is.element("stringr", installed.packages()[,1]))
  install.packages("stringr",repos="http://cran.rstudio.com")
if (!is.element("rvest", installed.packages()[,1]))
  install.packages("rvest",repos="http://cran.rstudio.com")
if (!is.element("xml2", installed.packages()[,1]))
  install.packages("xml2",repos="http://cran.rstudio.com")
 if (!is.element("tidyr", installed.packages()[,1]))
  install.packages("tidyr",repos="http://cran.rstudio.com")
if (!is.element("curl", installed.packages()[,1]))
  install.packages("curl",repos="http://cran.rstudio.com")
if (!is.element("stargazer", installed.packages()[,1]))
  install.packages("stargazer",repos="http://cran.rstudio.com")
if (!is.element("stringi", installed.packages()[,1]))
  install.packages("stringi",repos="http://cran.rstudio.com")
if (!is.element("scales", installed.packages()[,1]))
  install.packages("scales",repos="http://cran.rstudio.com")
if (!is.element("kableExtra", installed.packages()[,1]))
  install.packages("kableExtra",repos="http://cran.rstudio.com")
if (!is.element("knitr", installed.packages()[,1]))
  install.packages("knitr",repos="http://cran.rstudio.com")

@@

#Load libraries
library("dplyr")
library("rvest")
library("tidyr")
library("ggplot2")
library("stargazer")
library("ggpubr")
library("reshape2")
library("stringr")
library("scales")
library("knitr")
library("kableExtra")

@@

#Custom functions for Case Study 2
#Please open MSDS6306_Final_Case_Study_Functions.R for more details
#Last modified 11/26/17

source('MSDS6306_Final_Case_Study_Functions.R')

@@

# 2A: Read in CSV
filepath = 'C:\\Users\\Jose\\Downloads\\Case_Study_2\\CaseStudy2_MSDS'
dataset_raw <- read.csv(paste(filepath,'Procrastination.csv',sep='\\'))

@@

```{r Question4 Preliminary Analysis, warning=FALSE}

@@

# 4B:
#statistics table
stargazer(resp_full[,c('Age','Annual_Inc','HDI','DP_Avg','AIP_Avg','GP_Avg','SWLS_Avg')],
					summary.stat=c('n','min','p25','median','p75','max','mean','sd'),type='text')

@@

h1 = gghistogram(resp_full,x='Age',y='..count..',
								 bins=10,
								 fill='blue',
								 size=2,
								 title='Histogram of Age',
								 color='white',
								 ylab='Count'
)

h1 = h1 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5))

h2 = gghistogram(resp_full,x='Annual_Inc',y='..count..',
								 fill='blueviolet',
								 size=2,
								 bins=25,
								 title='Histogram of Annual Income',
								 color='white',
								 ylab='Count',
								 xlab='Annual Income'
)

Annual_Inc_Clean = resp_full[which(!is.na(resp_full$Annual_Inc)),'Annual_Inc']

h2 = h2 + font('xy.text',size=12) + 
  theme(plot.title=element_text(hjust=0.5)) +
  rotate_x_text(30) +
  scale_x_continuous(label=dollar_format(),breaks = round(seq(min(Annual_Inc_Clean), max(Annual_Inc_Clean), by = 50000),1))

h3 = gghistogram(resp_full,x='HDI',y='..count..',
								 bins=35,
								 fill='cadetblue3',
								 size=2,
								 title='Histogram of HDI',
								 color='white',
								 ylab='Count'
)

h3 = h3 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5))

@@

h4 = ggboxplot(metrics,x='Variable',
							 y='Value',
							 color='Variable',
							 palette='jco',
							 size=1,
							 xlab='')

h4 = h4 + font('xy.text',size=12) + theme(plot.title=element_text(hjust=0.5)) +
  rotate_x_text(30)

ggarrange(h1,h3,
					h2,h4,
					nrow=2,
					ncol=2)

@@

#For the codebook only
#These are the job assignments we subjectively made to get the top10 job counts shown:
top_jobs = match_list(resp_full$Current_Occ,findtext=keywords$title)

for (i in 1:length(top10Jobs$title)) {
print(paste(tolower(as.character(top10Jobs$title[i])),'<-', unique(unique(top_jobs[[i]][,2]))))
}

# Frequencies per column 
# Unique distributions

# Gender
gender_table = as.data.frame(table(resp_full$Gender))
colnames(gender_table) = c('Gender','Count')
kable(gender_table,row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:dim(gender_table)[1],bold=T,color='white',background='darkred')

# WorkStatus
work_table = as.data.frame(table(resp_full$Work_Status))
colnames(work_table) = c('Status','Count')
work_table = work_table[order(work_table$Count,decreasing=TRUE),]
kable(work_table,row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options=c('striped','condensed'),full_width=FALSE)%>%
  row_spec(row=1:dim(work_table)[1],bold=T,color='white',background='darkred')

#Distributions across Gender and Work Status
genderwork_table = as.data.frame(table(resp_full$Gender,resp_full$Work_Status))
colnames(genderwork_table) = c('Gender','Work_Status','Count')
genderwork_table = genderwork_table[order(genderwork_table$Count,decreasing=TRUE),]
kable(genderwork_table,row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:dim(genderwork_table)[1],bold=T,color='white',background='darkred')

kable(top10Jobs,row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:dim(top10Jobs)[1],bold=T,color='white',background='darkred')

@@

countryCt = as.data.frame(table(resp_full$Country_Res))
colnames(countryCt) = c('Country','Count')
sortedCC = countryCt[order(countryCt$Count, decreasing = TRUE),]
kable(head(sortedCC,20),row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:20,bold=T,color='white',background='darkred')
# 4E:

@@

match_yes = sum(resp_full$Self_Score == 'yes' & resp_full$Others_Score == 'yes')
match_no = sum(resp_full$Self_Score == 'no' & resp_full$Others_Score == 'no')
match_either = as.data.frame(cbind(match_yes,match_no))
colnames(match_either) = c('Others Agree I Procrastinate','Others Agree I Do Not Procrastinate')
kable(match_either,row.names=FALSE,format='html')%>%
  kable_styling(bootstrap_options='striped',full_width=FALSE)%>%
  row_spec(row=1:1,bold=T,color='black',background='beige')%>%
  column_spec(1:2,width='1cm')
